% Section 01 - Introduction

Manipulating physical systems as a consequence of light engagements inaugurated an astonishing scope of twentieth-century physics namely quantum optics \cite{grynberg10}.
Quantum optics have dragged research attention in the disciplines of optoelectronics \cite{liu16,wijesekara20,tao21}, sensing \cite{rodrigo2015,pirandola18,hapuarachchi2018}, energy harvesting \cite{yuan16,sun18},
quantum computing \cite{huh15,slussarenko19,andersen21}, bio-information \cite{marais18,bian20}, and abundant specialities of recent technologies \cite{rivera20}.
The studies on quantum optics of nanostructures were centered on metamaterials \cite{shalaev07,si14}, quantum plasmonic effects \cite{hapuarachchi19,perera20}, lasers and amplifiers \cite{zhang05,chow13}, quantum cavity physics \cite{tsang10,devi20}.
However, over the past few years, the foremost aims for examining nanostructures under external radiation were focused on understanding their transport characteristics \cite{kitagawa11,zhou11,kibis14,pervishko15,morina15,dehghani15,dini16,wackerl20}.

The significance of describing fundamental mechanisms taking place in charge transport is that they will pave the way to invent new nanoelectronic devices and optimize their performance \cite{premaratne21}.
Among these works, most studies have acknowledged the driving field as a perturbation field \cite{pervishko15,morina15} that is not applicable for systems under high-intensity illuminations \cite{grifoni98,wackerl20}.
When a high intensity electromagnetic field account with a perturbation method, the number of higher-order interaction terms need to be recognized gets escalate. Then a more accurate and powerful concept need to be adopted and we need to treat the interacting fermion system and the radiation as a one unique quantum system (dressed system) \cite{morina15,cohen98,scully01}. On account of the transport characteristics of dressed nanostructures, they are still expecting extensive analysis.

Theoretical analyses of the transport properties of dressed fermions systems were recently reported in Refs. \cite{kibis14,morina15,wackerl20} where a general expression for Floquet-Drude conductivity has been derived in a fully closed analytical form in Ref. \cite{wackerl20}, introducing a novel type of Green’s functions namely four-times Green’s functions. As a consequence, the established formalism introduces a novel technique to exploit the transport attributes of nanostructures by an intense dressing field.

At the other end, quantum Hall effect \cite{girvin90} observed for two-dimentional fermions systems at low temperatures under strong stationary magnetic field manifest remarkable magneto-transport behaviors and transport properties of these systems attracted many researches attention in experimental \cite{allerman95,tieke97,pan05} and theoretical \cite{ando72,ando74_1,ando74_2,ando74_3,ando74_4,ando82,endo09} point of view.
Akira Endo \textit{et al.} \cite{endo09} previously presented, the calculations of longitudinal and transverse conductivity tensor components and their relationship in a quantum Hall system and these theoretical calculations are well-suited with the experimental observations while other former studies yields a semi-elliptical broadening for Landau levels and gives less fitting interpretations for the empirical results \cite{endo09}.

In contrast, more fascinating transport phenomena can be achieved by creating a quantum Hall system using a nonoscillating magnetic field and simultaneously applying a dressing field.
Whilst there exist a number of leading theories devoted to the calculation of conductivity tensor elements in quantum Hall systems \cite{ando74_1,ando82,endo09}, they have not been utilized to describe the optical manipulation of charge transport in the quantum Hall systems.
Furthermore, K. Dini \textit{et al.} \cite{dini16} have recently investigated the one-directional conductivity behavior of dressed quantum Hall systems, and they have not adopted the state-of-the-art model to describe the conductivity in a quantum Hall system. In their study, they used the conductivity models from Refs. \cite{ando74_1,ando82} and as mentioned in A. Endo \textit{et al.} work \cite{endo09} those models yields a semi-elliptical broadening for Landau levels and gives barely fitting representations for the experimental findings.

In the present analysis, we report a robust mathematical model for dressed two-dimensional electron gas(2DEG) unveiled to another nonoscillating magnetic field.
A stationary magnetic field is applied perpendicularly across the surface of 2DEG system and the orbital motion of electrons becomes completely quantized, and the energy spectrum becomes discrete by creating Landau levels \cite{landau30}.
Such a singular system is known as a two-dimentional quantum Hall system and in this study, we explicitly calculate the longitudinal  ($\sigma^{xx},\sigma^{yy}$) components of the conductivity tensor in the periodically driven quantum Hall systems by developing a generalized analytical description to identify transport characteristics of dressed quantum Hall systems using Floquet-Drude conductivity \cite{wackerl20}.
Finally, we demonstrate that our generalized model is agreed with state-of-the-art conductivity model \cite{endo09} already developed for specialized quantum Hall systems that have been considered without the external dressing field. 
Moreover, optical manipulation can be used as a mechanism to utilize transport behavior in numerous two-dimentional nanostructures which serve as a basis for nanoelectronic devices and we believe that our theoretical analysis and visual depictions of numerical results can be used to understand the basic structure and optimize the performance of nanoscale quantum devices.

The paper is organized as follows. In Sec.  \ref{sec_schrodinger_problem}, we introduce our dressed quantum Hall system and the exact wave function solutions for the given configuration. Sec. \ref{sec_floquet_theory}, provides the Floquet theory interpretation of these wave functions.
We introduce Floquet Fermi golden rule for quantum Hall system in Sec. \ref{sec_inverse_scattering_time}, and we use it in Sec. \ref{sec_floquet_drude_conductivity} to derive analytical expressions for longitudinal components of conductivity.
The derived theoritical model is further analyzed numerically using empherical system parameters and compared with previous studies in Sec. \ref{sec_manipulate_conductivity}, followed by concluding remarks in Sec. \ref{sec_conclusions}.
